\LARGE{\bf{Natural variation in teosinte at the domestication locus \emph{teosinte branched1} (\emph{tb1})}}\footnotemark

### 2014-08-27 ResponseToReview.tex

15) Page 7 lines 22 - 23: "We used genotyping and covariance data from Pyhajarvi et al. (2013) for BayEnv" what kind of dataset is this? Teosinte?\\

\res{We have clarified the dataset in the paper: ``We used teosinte (ssp. \emph{parviglumis} and ssp. \emph{mexicana} genotyping and covariance data from Pyh{\"a}j{\"a}rvi \emph{et al.} (2013) for BayEnv, with the \emph{Hopscotch} insertion coded as an additional SNP. SNP data from Pyh{\"a}j{\"a}rvi \emph{et al.} (2013) were obtained using the MaizeSNP50 BeadChip and Infinium® HD Assay (Illumina, San Diego, CA, USA)."}

16) Page 8 lines 20 - 21:" We created haplotype blocks using a custom Perl script that grouped SNPs separated by less than 5kb into haplotypes." Does LD data in your parviglumus support 5Kb?\\

\res{hmm. Matt why did you use 5kb when you did this for your study?}
\jri{read Matt's paper, explain to reviewer}
\lev{I cannot find it explicitly stated in the paper. My assumption is that since STRUCTURE doesn't account for physical linkage you grouped things into chunks of 5kb chunks to try to elimiate the effects of physical linkage since LD decays in maize in ~1kb if I remember correctly. Is this correct? I've written it in this way, so let me know if this is wrong}

### 2014-08-27 ResponseToReview.tex

15) Page 7 lines 22 - 23: "We used genotyping and covariance data from Pyhajarvi et al. (2013) for BayEnv" what kind of dataset is this? Teosinte?\\

\res{We have clarified the dataset in the paper: ``We used teosinte (ssp. \emph{parviglumis} and ssp. \emph{mexicana} genotyping and covariance data from Pyh{\"a}j{\"a}rvi \emph{et al.} (2013) for BayEnv, with the \emph{Hopscotch} insertion coded as an additional SNP. SNP data from Pyh{\"a}j{\"a}rvi \emph{et al.} (2013) were obtained using the MaizeSNP50 BeadChip and Infinium® HD Assay (Illumina, San Diego, CA, USA)."}

16) Page 8 lines 20 - 21:" We created haplotype blocks using a custom Perl script that grouped SNPs separated by less than 5kb into haplotypes." Does LD data in your parviglumus support 5Kb?\\

\res{Previous work has shown that LD decays in maize in 2000bp, on average. We wanted to avoid picking up signals of linkage due to physical linkage in our analyses  (STRUCTURE does not account for linkage due to physical distance), thus we grouped SNPs that were separated by less than a certain distance (5kb) into haplotype blocks in hopes that we would be grouping SNPs that would otherwise give signals of linkage due to physical linkage. We have clarified this point in the text, page 9, lines 182-186: ``Since STRUCTURE does not account for LD due to physical linkage we created haplotype blocks using a custom Perl script from Hufford \emph{et al.} (2013) that grouped SNPs separated by less than 5kb into haplotypes (Hufford \emph{et al.} 2011). LD decays on average in 2000bp in maize (Remington \emph{et al.} 2001), thus we feel comfortable using haplotype blocks of 5kb in order to circumvent picking up evidence of physical linkage in our STRUCTURE analyses."}

\res{hmm. Matt why did you use 5kb when you did this for your study?}
\jri{read Matt's paper, explain to reviewer}
\lev{I cannot find it explicitly stated in the paper. My assumption is that since STRUCTURE doesn't account for physical linkage you grouped things into chunks of 5kb chunks to try to elimiate the effects of physical linkage since LD decays in maize in ~2kb if I remember correctly. Is this correct? I've written it in this way, so let me know if this is wrong}

### 2014-08-27 manuscript.tex
Edits to response to reviewer 2, text, refs
Edits concerning STRUCTURE analyses; including response to review,
methods, and references

We examined evidence of introgression on chromosome 1 in these same four populations (EjuA, EjuB, MSA, SLO) using STRUCTURE \citep{Falush2003} and phased data from \citet{Pyhajarvi2013}, combined with the corresponding SNP data from a diverse panel of 282 maize lines \citep{Cook2012}. SNPs were anchored in a modified version of the IBM genetic map \citep{Gerke2013}. We created haplotype blocks using a custom Perl script that grouped SNPs separated by less than 5kb into haplotypes. We ran STRUCTURE at K=2 under the linkage model, performing 3 replicates with an MCMC burn-in of 10,000 steps and 50,000 steps post burn-in.

>>>>

We examined evidence of introgression on chromosome 1 in these same four populations (EjuA, EjuB, MSA, SLO) using STRUCTURE \citep{Falush2003} and phased data from \citet{Pyhajarvi2013}, combined with the corresponding SNP data from a diverse panel of 282 maize lines \citep{Cook2012}. SNPs were anchored in a modified version of the IBM genetic map \citep{Gerke2013}. Since STRUCTURE does not account for LD due to physical linkage we created haplotype blocks using a custom Perl script from Hufford \emph{et al.} (2013) that grouped SNPs separated by less than 5kb into haplotypes \citep{Hufford2013}. LD decays on average in 2000bp in maize \citep{Remington2001}, thus we feel comfortable using haplotype blocks of 5kb in order to circumvent picking up evidence of physical linkage in our STRUCTURE analyses. We ran STRUCTURE at K=2 under the linkage model, performing 3 replicates with an MCMC burn-in of 10,000 steps and 50,000 steps post burn-in.
